quollr: An R Package for Visualizing \(2-D\) Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-19 paper-quollr.tex
Corrected the code
Updated paper
New version

\begin{verbatim}
#> $a1
#> [1] 0.1089367
#> 
#> $a2
#> [1] 0.09434198
#> 
#> $bins
#> [1] 12 13
#> 
#> $start_point
#> [1] -0.10000000 -0.09382762
#> 
#> $centroids
#> # A tibble: 156 x 3
#>    hexID      c_x     c_y
#>    <int>    <dbl>   <dbl>
#>  1     1 -0.1     -0.0938
#>  2     2  0.00894 -0.0938
#>  3     3  0.118   -0.0938
#>  4     4  0.227   -0.0938
#>  5     5  0.336   -0.0938
#>  6     6  0.445   -0.0938
#>  7     7  0.554   -0.0938
#>  8     8  0.663   -0.0938
#>  9     9  0.771   -0.0938
#> 10    10  0.880   -0.0938
#> # i 146 more rows
#> 
#> $hex_poly
#> # A tibble: 936 x 3
#>    hex_poly_id        x       y
#>          <int>    <dbl>   <dbl>
#>  1           1 -0.1     -0.0309
#>  2           1 -0.154   -0.0624
#>  3           1 -0.154   -0.125 
#>  4           1 -0.1     -0.157 
#>  5           1 -0.0455  -0.125 
#>  6           1 -0.0455  -0.0624
#>  7           2  0.00894 -0.0309
#>  8           2 -0.0455  -0.0624
#>  9           2 -0.0455  -0.125 
#> 10           2  0.00894 -0.157 
#> # i 926 more rows
#> 
#> $data_hb_id
#> # A tibble: 3,750 x 4
#>      emb1   emb2    ID hb_id
#>     <dbl>  <dbl> <int> <int>
#>  1 0.276  0.915      1   136
#>  2 0.927  0.347      2    70
#>  3 0.810  0.242      3    45
#>  4 0.137  0.657      5    99
#>  5 0.476  0.799      6   114
#>  6 0.0485 0.0657     7    26
#>  7 0.737  0.851      9   129
#>  8 0.833  0.224     10    45
#>  9 0.909  0.371     11    70
#> 10 0.0890 0.194     12    38
#> # i 3,740 more rows
#> 
#> $std_cts
#> # A tibble: 72 x 3
#>    hb_id     n std_counts
#>    <int> <int>      <dbl>
#>  1    13     2     0.0194
#>  2    14    81     0.786 
#>  3    15    56     0.544 
#>  4    16    55     0.534 
#>  5    18     2     0.0194
#>  6    26    70     0.680 
#>  7    27    78     0.757 
#>  8    28    86     0.835 
#>  9    29     5     0.0485
#> 10    30    54     0.524 
#> # i 62 more rows
#> 
#> $tot_bins
#> [1] 156
#> 
#> $non_bins
#> [1] 72
#> 
#> $pts_bins
#> # A tibble: 72 x 2
#>    hexID pts_list     
#>    <int> <named list> 
#>  1   136 <int [3,750]>
#>  2    70 <int [3,750]>
#>  3    45 <int [3,750]>
#>  4    99 <int [3,750]>
#>  5   114 <int [3,750]>
#>  6    26 <int [3,750]>
#>  7   129 <int [3,750]>
#>  8    38 <int [3,750]>
#>  9   111 <int [3,750]>
#> 10    14 <int [3,750]>
#> # i 62 more rows
#> 
#> attr(,"class")
#> [1] "hex_bin_obj"
\end{verbatim}

@@

--\textgreater{}
--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}
--\textgreater{}

--\textgreater{}

--\textgreater{}

--\textgreater{}

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/fig-limb-mse-1} \end{figure}

>>>>

\begin{verbatim}
#> $a1
#> [1] 0.1089367
#> 
#> $a2
#> [1] 0.09434198
#> 
#> $bins
#> [1] 12 13
#> 
#> $start_point
#> [1] -0.10000000 -0.09382762
#> 
#> $centroids
#> # A tibble: 156 x 3
#>    hexID      c_x     c_y
#>    <int>    <dbl>   <dbl>
#>  1     1 -0.1     -0.0938
#>  2     2  0.00894 -0.0938
#>  3     3  0.118   -0.0938
#>  4     4  0.227   -0.0938
#>  5     5  0.336   -0.0938
#>  6     6  0.445   -0.0938
#>  7     7  0.554   -0.0938
#>  8     8  0.663   -0.0938
#>  9     9  0.771   -0.0938
#> 10    10  0.880   -0.0938
#> # i 146 more rows
#> 
#> $hex_poly
#> # A tibble: 936 x 3
#>    hex_poly_id        x       y
#>          <int>    <dbl>   <dbl>
#>  1           1 -0.1     -0.0309
#>  2           1 -0.154   -0.0624
#>  3           1 -0.154   -0.125 
#>  4           1 -0.1     -0.157 
#>  5           1 -0.0455  -0.125 
#>  6           1 -0.0455  -0.0624
#>  7           2  0.00894 -0.0309
#>  8           2 -0.0455  -0.0624
#>  9           2 -0.0455  -0.125 
#> 10           2  0.00894 -0.157 
#> # i 926 more rows
#> 
#> $data_hb_id
#> # A tibble: 3,750 x 4
#>      emb1   emb2    ID hb_id
#>     <dbl>  <dbl> <int> <int>
#>  1 0.276  0.915      1   136
#>  2 0.927  0.347      2    70
#>  3 0.810  0.242      3    45
#>  4 0.137  0.657      5    99
#>  5 0.476  0.799      6   114
#>  6 0.0485 0.0657     7    26
#>  7 0.737  0.851      9   129
#>  8 0.833  0.224     10    45
#>  9 0.909  0.371     11    70
#> 10 0.0890 0.194     12    38
#> # i 3,740 more rows
#> 
#> $std_cts
#> # A tibble: 72 x 3
#>    hb_id     n std_counts
#>    <int> <int>      <dbl>
#>  1    13     2     0.0194
#>  2    14    81     0.786 
#>  3    15    56     0.544 
#>  4    16    55     0.534 
#>  5    18     2     0.0194
#>  6    26    70     0.680 
#>  7    27    78     0.757 
#>  8    28    86     0.835 
#>  9    29     5     0.0485
#> 10    30    54     0.524 
#> # i 62 more rows
#> 
#> $tot_bins
#> [1] 156
#> 
#> $non_bins
#> [1] 72
#> 
#> $pts_bins
#> # A tibble: 72 x 2
#>    hb_id pts_list  
#>    <int> <list>    
#>  1    13 <int [2]> 
#>  2    14 <int [81]>
#>  3    15 <int [56]>
#>  4    16 <int [55]>
#>  5    18 <int [2]> 
#>  6    26 <int [70]>
#>  7    27 <int [78]>
#>  8    28 <int [86]>
#>  9    29 <int [5]> 
#> 10    30 <int [54]>
#> # i 62 more rows
#> 
#> attr(,"class")
#> [1] "hex_bin_obj"
\end{verbatim}

@@

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/fig-limb-mse-1} \end{figure}

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-20-1}
